---
title: "OUR PALESTINIAN FAMILIES’ FUNDRAISERS"
execute:
  message: false
  error: false
  warning: false
  echo: false
format: 
  html:
    toc: false
    # link-external-icon: true
    link-external-newwindow: true
---
<br>

### Which family/campaign should I donate to?

Any! We are connected to each of these families, and every one is in dire need of help. Each of these families is someone we know personally, or is connected to our people.

```{r}

library(tidyverse)
library(googledrive)
library(googlesheets4)
library(rvest)
library(bslib)
library(bsicons)
library(gt)

library(gtExtras)

```


```{r}
##| eval: false
##| cache: true
# 
source("gfm-data.R")

```




```{r cleaning df}
##| eval: false
#| echo: false
#| include: false


x <- test_tib %>% 
  dplyr::filter(!is.na(total_goal_amount))

# final_table <-  x %>% 
#   dplyr::mutate(amount_raised_num = parse_number(money_raised)) %>% 
#   dplyr::mutate(currency = str_extract(money_raised, "[€|$|kr|£]")) %>% 
#   dplyr::mutate(currency_abv = dplyr::case_when(
#     currency == "$" & is_canadian == FALSE ~ "USD",
#     currency == "$" & is_canadian == TRUE ~ "CAD",    
#     currency == "€" ~ "EUR",
#     currency == "£" ~ "GBP",
#     currency == "k" & link == 
#       "https://www.gofundme.com/f/4-months-separates-between-life-and-death-and-we" ~ "SEK",
#     currency == "k" & link == "https://www.gofundme.com/f/help-my-sister-and-her-family-escape-the-war-in-gaza" ~ "NOK",
#     TRUE ~ NA_character_
#   )) %>% 
#   dplyr::mutate(percent_of_goal = amount_raised_num / total_goal_amount*100) %>% 
#   dplyr::mutate(fund_parameter = str_sub(link, start = 28L)) %>% 
#   dplyr::left_join( sheet_gaza %>% 
#                       # removing fund with broken link for now
#                       janitor::clean_names() %>% 
#                      dplyr::select(1:2, status, fund_parameter),
#                    by = "fund_parameter") %>% 
#   dplyr::arrange(desc(status), percent_of_goal) %>%  
#   dplyr::mutate(link_text = str_wrap(gfm_link, width = 18)) %>% 
#   # dplyr::mutate(uuid = str_sub(link, start = 19L)) %>% 
#   dplyr::select(link, link_text,
#                 total_num_donations,currency_abv, amount_raised_num, 
#                 percent_of_goal, 
#                 total_num_donations_24_hours:money_raised_24_hours)



```


```{r removing daily numbers from table}
##| eval: false
#| echo: false
#| include: false

final_table1 <-  x %>% 
  dplyr::mutate(amount_raised_num = money_raised) %>% 
  # dplyr::mutate(currency = str_extract(money_raised, "[€|$|kr|£]")) %>% 
  dplyr::mutate(currency_abv = case_when(
    currency == "Other" ~ "NOK",
    TRUE ~ currency)) %>% 
  dplyr::mutate(percent_of_goal = amount_raised_num / total_goal_amount*100) %>% 
  dplyr::mutate(fund_parameter = str_sub(link, start = 28L)) %>% 
  dplyr::left_join( sheet_gaza %>% 
                      # removing fund with broken link for now
                      janitor::clean_names() %>% 
                     dplyr::select(1:2, status, fund_parameter),
                   by = "fund_parameter") %>%
  dplyr::arrange(desc(status), percent_of_goal) %>%  
  dplyr::mutate(link_text = str_wrap(gfm_link, width = 18)) %>% 
  # dplyr::mutate(uuid = str_sub(link, start = 19L)) %>% 
  dplyr::select(fund_parameter, link, link_text,
                # total_num_donations,
                currency_abv, amount_raised_num, 
                percent_of_goal)


```


```{r}
##| eval: false

data_write_back <- final_table1 %>% 
  dplyr::mutate(link = str_sub(link, start = 28L)) %>% 
  dplyr::select(link, amount_raised_num) %>% 
  dplyr::mutate(date = now()) 


googlesheets4::sheet_append(
    ss = ss1,
    sheet = "data",
    data = data_write_back
  )

```


```{r adding daily numbers}
##| eval: false

sheet_gaza_data <- read_sheet(ss1,
                              sheet = "data")

num_funds <- nrow(all_gfm_links) 

daily_numbers <- sheet_gaza_data %>% 
  dplyr::filter(date > today() - days(4)) %>% 
  dplyr::arrange(desc(date)) %>% 
  dplyr::group_by(link) %>% 
  dplyr::mutate(row_n = row_number()) %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(row_n %in% c(1,2)) %>% 
  # dplyr::filter(date > as.Date("2024-09-13")) %>% 
  dplyr::arrange(link, date) %>% 
  dplyr::mutate(lagged_val = lag(amount_raised_num)) %>% 
  dplyr::mutate(daily_change = amount_raised_num - lagged_val) %>% 
  dplyr::mutate(filt_this = rep(c(FALSE, TRUE), num_funds)) %>% 
  dplyr::filter(filt_this == TRUE) %>% 
  dplyr::select(link, daily_change)

weekly_numbers <- sheet_gaza_data %>% 
  dplyr::filter(date > today() - days(7)) %>% 
  dplyr::group_by(link) %>% 
  dplyr::summarise(
    weekly_total = 
      max(amount_raised_num) - min(amount_raised_num)
  ) %>%  
  dplyr::ungroup()

biweekly_numbers <- sheet_gaza_data %>% 
  dplyr::filter(date > today() - days(14)) %>% 
  dplyr::group_by(link) %>% 
  dplyr::summarise(
    biweekly_total = 
      max(amount_raised_num) - min(amount_raised_num)
  ) %>%  
  dplyr::ungroup()

monthly_numbers <- sheet_gaza_data %>% 
  dplyr::filter(date > today() - days(31)) %>% 
  dplyr::group_by(link) %>% 
  dplyr::summarise(
    monthly_total = 
      max(amount_raised_num) - min(amount_raised_num)
  ) %>%  
  dplyr::ungroup()


aggregate_data <- sheet_gaza %>% 
  janitor::clean_names() %>% 
  dplyr::filter(!person_family %in% c("Jenna/Hashem"),
                status != "CLOSED / NOT ACCEPTING DONATIONS") %>%   
  dplyr::filter(str_detect(links, "gofund"))  %>% 
  dplyr::mutate(fund_parameter = str_squish(fund_parameter)) %>% 
  dplyr::select(gfm_link:status) %>% 
  dplyr::left_join(weekly_numbers,
                   by = join_by(fund_parameter == link)) %>% 
  dplyr::left_join(biweekly_numbers,
                   by = join_by(fund_parameter == link)) %>%  
  dplyr::left_join(monthly_numbers,
                   by = join_by(fund_parameter == link)) %>% 
  dplyr::arrange(desc(status), monthly_total) %>%  
  dplyr::left_join(final_table1 %>% 
                       dplyr::select(fund_parameter, currency_abv),
                   join_by(fund_parameter)) %>% 
  dplyr::select(-fund_parameter)  



googlesheets4::sheet_write(
    ss = ss1,
    sheet = "aggregate-data",
    data = aggregate_data
  )

# most recent row with a number for donation
# sheet_gaza_data %>% 
#   dplyr::filter(str_detect(total_num_donations, "[0-9]")) %>% 
#   dplyr::group_by(link) %>% 
#   dplyr::filter(date > today() - days(4)) %>%
#   dplyr::arrange(desc(date)) %>% 
#   dplyr::group_by(link) %>% 
#   dplyr::mutate(row_n = row_number()) %>% 
#   dplyr::ungroup() %>% 
#   dplyr::filter(row_n %in% c(1)) %>% View()

final_table <- final_table1 %>% 
  dplyr::left_join(daily_numbers,
                   join_by(fund_parameter == link)) %>% 
  dplyr::select(-fund_parameter)

```


```{r sum of currencies}
##| eval: false
sum_all_donations_in_usd <- final_table %>%
  dplyr::filter(currency_abv == "USD") %>% 
  summarise(sum(amount_raised_num)) %>%
  as.numeric() %>%
  format(big.mark = ",")

sum_all_donations_in_usd_24 <- final_table %>%
  dplyr::filter(currency_abv == "USD") %>% 
  summarise(sum(daily_change)) %>%
  as.numeric() %>%
  format(big.mark = ",")

# sum_all_donations_in_cad <- final_table %>%
#   dplyr::filter(currency_abv == "CAD") %>% 
#   summarise(sum(amount_raised_num)) %>%
#   as.numeric() %>%
#   format(big.mark = ",")

# sum_all_donations_in_cad_24 <- final_table %>%
#   dplyr::filter(currency_abv == "CAD") %>% 
#   summarise(sum(daily_change)) %>%
#   as.numeric() %>%
#   format(big.mark = ",")

sum_all_donations_in_eur <- final_table %>%
  dplyr::filter(currency_abv == "EUR") %>% 
  summarise(sum(amount_raised_num)) %>%
  as.numeric() %>%
  format(big.mark = ",")


sum_all_donations_in_eur_24 <- final_table %>%
  dplyr::filter(currency_abv == "EUR") %>% 
  summarise(sum(daily_change)) %>%
  as.numeric() %>%
  format(big.mark = ",")

sum_all_donations_in_gbp <- final_table %>%
  dplyr::filter(currency_abv == "GBP") %>% 
  summarise(sum(amount_raised_num)) %>%
  as.numeric() %>%
  format(big.mark = ",")

sum_all_donations_in_gbp_24 <- final_table %>%
  dplyr::filter(currency_abv == "GBP") %>% 
  summarise(sum(daily_change)) %>%
  as.numeric() %>%
  format(big.mark = ",")

sum_all_donations_in_sek <- final_table %>%
  dplyr::filter(currency_abv == "SEK") %>% 
  summarise(sum(amount_raised_num)) %>%
  as.numeric() %>%
  format(big.mark = ",")

sum_all_donations_in_sek_24 <- final_table %>%
  dplyr::filter(currency_abv == "SEK") %>% 
  summarise(sum(daily_change)) %>%
  as.numeric() %>%
  format(big.mark = ",")

sum_all_donations_in_nok <- final_table %>%
  dplyr::filter(currency_abv == "NOK") %>% 
  summarise(sum(amount_raised_num)) %>%
  as.numeric() %>%
  format(big.mark = ",")

sum_all_donations_in_nok_24 <- final_table %>%
  dplyr::filter(currency_abv == "NOK") %>% 
  summarise(sum(daily_change)) %>%
  as.numeric() %>%
  format(big.mark = ",")

num_funds_usd <- final_table %>%
  dplyr::filter(currency_abv == "USD") %>% 
  nrow()

num_funds_usd_24 <- final_table %>%
  dplyr::filter(currency_abv == "USD") %>% 
  dplyr::filter(daily_change > 0.01) %>% 
  nrow()

# num_funds_cad <- final_table %>%
#   dplyr::filter(currency_abv == "CAD") %>% 
#   nrow()
# 
# num_funds_cad_24 <- final_table %>%
#   dplyr::filter(currency_abv == "CAD") %>% 
#   dplyr::filter(daily_change > 0.01) %>% 
#   nrow()

num_funds_euro <- final_table %>%
  dplyr::filter(currency_abv == "EUR") %>% 
  nrow()

num_funds_euro_24 <- final_table %>%
  dplyr::filter(currency_abv == "EUR") %>% 
  dplyr::filter(daily_change > 0.01) %>% 
  nrow()

num_funds_gbp <- final_table %>%
  dplyr::filter(currency_abv == "GBP") %>% 
  nrow()

num_funds_gbp_24 <- final_table %>%
  dplyr::filter(currency_abv == "GBP") %>% 
  dplyr::filter(daily_change > 0.01) %>% 
  nrow()

num_funds_sek <- final_table %>%
  dplyr::filter(currency_abv == "SEK") %>% 
  nrow()

num_funds_sek_24 <- final_table %>%
  dplyr::filter(currency_abv == "SEK") %>% 
  dplyr::filter(daily_change > 0.01) %>% 
  nrow()

num_funds_nok <- final_table %>%
  dplyr::filter(currency_abv == "NOK") %>% 
  nrow()

num_funds_nok_24 <- final_table %>%
  dplyr::filter(currency_abv == "NOK") %>% 
  dplyr::filter(daily_change > 0.01) %>% 
  nrow()

```


```{r}
# 
# library(qrcode)
# 
# 
# links_qr <- all_gfm_links %>%
#   dplyr::select(link = links)
# 
# row_n_qr <- final_table %>%
#   dplyr::select(uuid)
# 
# 
# for(i in 1:num_funds){
# 
#   link = as.character(links_qr[i,1])
# 
#   rn = as.character(row_n_qr[i,1])
# 
#   png(filename = str_glue("qr-codes/{rn}.png"))
# 
#   plot(qr_code(link ,
#         ecl = "Q") %>%
#   qrcode::add_logo(
#     logo = "images/cfg-logo-new.png",
#     ecl = "L",
#     hjust = "c",
#     vjust = "c"
#   ))
# 
#   plot(qr_code(link ,
#         ecl = "Q") %>%
#   qrcode::add_logo(
#     logo = "images/cfg-logo-new.png",
#     ecl = "L",
#     hjust = "c",
#     vjust = "c"
#   ))
# 
# }

# Table below updated on `r format(lubridate::now("UTC") - hours(8), "%B %d, %Y")` at `r paste0(format(lubridate::now("UTC") - hours(8), "%I:%M %p"), " PST") `

```


#### *CLICK THRU* to donate or share

Table below updated on `r format(lubridate::now("UTC") - hours(8), "%B %d, %Y")` at `r paste0(format(lubridate::now("UTC") - hours(8), "%I:%M %p"), " PST") `


```{r final table}
##| eval: false
#| column: screen

chuffed_links <- tibble(
  link = c("https://chuffed.org/project/artistmohammedalassar",
           "https://chuffed.org/project/122413-a-new-chapter-in-our-journey-help-mahmoud-continue-his-education-amidst-the-crisis-in-gaza",
           "https://chuffed.org/project/helpmalak",
           "https://chuffed.org/project/rahmasfamily",
           "https://chuffed.org/project/135758-stand-with-saeed-and-his-family",
           "https://chuffed.org/project/141405-hope-for-nidaa",
           "https://chuffed.org/project/helpmaryam"),
  link_text = c("Mohammed and his wife",
                "Help Mahmoud evacuate Gaza",
                "Help Malak and her family escape",
                "Rahma and Family",
                "Saeed + Aya + their children",
                "Nedaa Oweida + family",
                "Maryam and Family"),
  # total_num_donations = c(NA, NA, NA, NA, NA, NA, NA),
  currency_abv = c("USD", "USD", "USD", "USD", "USD", "EUR", "USD"),
  amount_raised_num = c(NA, NA, NA, NA, NA, NA, NA),
  percent_of_goal = c(12.54, 95.11, 72.02, 65.30, 70.74, 11.18, 12.50),
  daily_change = c(NA, NA, NA, NA, NA, NA, NA)
)

# paypal_links <- tibble(
#   link = "https://www.paypal.com/paypalme/belaljasem",
#   link_text = "Help Malak and her family escape",
#   total_num_donations = NA,
#   currency_abv = "USD",
#   amount_raised_num = NA,
#   percent_of_goal = 0,
#   daily_change = NA
# )

link_text <- final_table %>%
  dplyr::bind_rows(chuffed_links) %>% 
  # dplyr::bind_rows(paypal_links) %>%   
  dplyr::pull(link_text) 

# format(lubridate::now(), "%B %d, %Y")
# format(lubridate::now(), "%I:%M %p %Z")


final_table %>% 
  dplyr::bind_rows(
    chuffed_links
  ) %>% 
  dplyr::select(-c(link_text)) %>% 
  # dplyr::relocate(uuid, .before = link) %>% 
  gt(
    ) %>%
  gt::fmt_url(
    columns = link, 
    label = link_text,
    color = "#fe1a2f"
  ) %>% 
  gt::tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = everything()
    )
  ) %>%   
  gt::cols_width(
    # total_num_donations ~ px(80),
    amount_raised_num ~ px(110),
    daily_change ~ px(100)
  ) %>% 
  gt::sub_missing(
    columns = everything(),
    rows = everything(),
    missing_text = ""
  ) %>% 
  gt::fmt_currency(
    columns = c(amount_raised_num, daily_change),
    currency = from_column(column = "currency_abv"),
    decimals = 0
  ) %>% 
  # gt::fmt_percent(columns = percent_of_goal,
  #                 decimals = 0) %>%
  gtExtras::gt_plt_bar_pct(
    column = percent_of_goal,
    labels = TRUE,
    scaled = TRUE,
    fill = "#01e2b4",
    height = 26,
    width = 132,
    font_style = "bold",
    font_size = "13px",
    decimals = 0,
    label_cutoff = 0
  ) %>%
  gt::cols_hide(
    c(currency_abv)
  ) %>%
  gt::tab_style(
    style = list(
      cell_borders(
        side = c("left", "right"),
        color = "#f4f4f4"
      )
    ),
    locations = cells_body(
      columns = c(amount_raised_num, percent_of_goal)
    )
  ) %>% 
  gt::cols_label(
    amount_raised_num = "Total amount raised",
    percent_of_goal = "Percent of goal reached",
    daily_change = paste0("Amount raised on ", format(lubridate::now("UTC") - lubridate::days(1), "%B %d")),
    # uuid = "QR Code",
    link = "Link to Fundraiser"
  ) %>% 
  gt::tab_options(table.width = pct(100),
                      # table.font.color = "#FFFFFF",
    table.background.color = "#FFFFFF",
    table.font.size = px(13),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    # table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent") %>% 
  gt::opt_css(
    css = "
    table tr:nth-child(odd) {
      background-color: white;
    }
      
    table tr:hover {
      background-color: lightgrey;
    }
    
    .cell-output-display {
      overflow-x: unset !important;
    }
    
    div#custom {
      overflow-x: unset !important;
      overflow-y: unset !important;
    }
    
    #custom .gt_col_heading {
      position: sticky !important;
      top: -5px !important;
      z-index: 10 !important;
    }
    "
  )



```

<br>

#### Total amount raised from all the current fundraising campaigns

```{r totals}
##| eval: false
#| column: screen
#| color: primary
#| theme: primary


vbs <- list(
  value_box(
    title = paste0("Total amount raised in Euros from ", num_funds_euro, " funds:"),
    # theme = "orange", # doesnt work must change this in scss file
    value = paste0("€", sum_all_donations_in_eur),
    icon = bs_icon("cash")
  ),
  value_box(
    title = paste0("Total amount raised in US Dollars from ", num_funds_usd, " funds:"),
    # theme = "#01e2b4",
    value = paste0("$", sum_all_donations_in_usd),
    icon = bs_icon("bank")
  ),
  # value_box(
  #   title = paste0("Total amount raised in Canadian Dollars from ", num_funds_cad, " funds:"),
  #   # theme = "#01e2b4",
  #   value = paste0("$", sum_all_donations_in_cad),
  #   icon = bs_icon("bank")
  # ),  
  value_box(
    title = paste0("Total amount raised in British Pounds from ", num_funds_gbp, " funds:"),
    # theme = "primary",
    value = paste0("£", sum_all_donations_in_gbp),
    icon = "cash"
  ),
  value_box(
    title = paste0("Total amount raised in Swedish krona from ", num_funds_sek, " funds:"),
    # theme = "light",
    value = paste0("kr", sum_all_donations_in_sek),
    icon = "cash"
  ),
  value_box(
    title = paste0("Total amount raised in Norwegian krone from ", num_funds_nok, " funds:"),
    # theme = "light",
    value = paste0("kr", sum_all_donations_in_nok),
    icon = "cash"
  )  
)

layout_column_wrap(
  width = "250px",
  fixed_width = TRUE,
  !!!vbs
)

```


#### Amount raised on `r format(lubridate::now("UTC") - lubridate::days(1), "%B %d, %Y")`

```{r totals 24}
##| eval: false
#| column: screen
#| color: primary
#| theme: primary


vbs1 <- list(
  value_box(
    title = paste0("Amount raised in Euros on ", format(lubridate::now("UTC") - lubridate::days(1), "%B %d, %Y"),
                   " from ", num_funds_euro_24, " funds:"),
    # theme = "orange", # doesnt work must change this in scss file
    value = paste0("€", sum_all_donations_in_eur_24),
    icon = bs_icon("cash")
  ),
  value_box(
    title = paste0("Amount raised in US Dollars on ", 
                   format(lubridate::now("UTC") - lubridate::days(1), "%B %d, %Y"),
                   " from ", num_funds_usd_24, " funds:"),
    # theme = "orange", # doesnt work must change this in scss file
    value = paste0("$", sum_all_donations_in_usd_24),
    icon = bs_icon("cash")
  ),  
  # value_box(
  #   title = paste0("Amount raised in Canadian Dollars on ", 
  #                  format(lubridate::now("UTC") - lubridate::days(1), "%B %d, %Y"),
  #                  " from ", num_funds_cad_24, " funds:"),
  #   # theme = "orange", # doesnt work must change this in scss file
  #   value = paste0("$", sum_all_donations_in_cad_24),
  #   icon = bs_icon("cash")
  # ),    
  value_box(
    title = paste0("Amount raised in British Pounds on ", 
                   format(lubridate::now("UTC") - lubridate::days(1), "%B %d, %Y"),
                   " from ", num_funds_gbp_24, " funds:"),
    # theme = "orange", # doesnt work must change this in scss file
    value = paste0("£", sum_all_donations_in_gbp_24),
    icon = bs_icon("cash")
  ),    
  value_box(
    title = paste0("Amount raised in Swedish krona on ", 
                   format(lubridate::now("UTC") - lubridate::days(1), "%B %d, %Y"),
                   " from ", num_funds_sek_24, " funds:"),
    # theme = "orange", # doesnt work must change this in scss file
    value = paste0("kr", sum_all_donations_in_sek_24),
    icon = bs_icon("cash")
  ),
  value_box(
    title = paste0("Amount raised in Norwegian krone on ", 
                   format(lubridate::now("UTC") - lubridate::days(1), "%B %d, %Y"),
                   " from ", num_funds_nok_24, " funds:"),
    # theme = "orange", # doesnt work must change this in scss file
    value = paste0("kr", sum_all_donations_in_nok_24),
    icon = bs_icon("cash")
  )  
)

layout_column_wrap(
  width = "250px",
  fixed_width = TRUE,
  !!!vbs1
)

```


[Link to latest currency conversion rates](https://www.bloomberg.com/markets/currencies)

